\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

There is not enough space in this margin to thank everyone who deserves to be thanked for being part of my PhD journey. It has been an amazing 4 years and I have had the pleasure of having many great friends during this time. In particular, I would like to start by thanking my friend and supervisor Jonathan Fraser who has been supporting me since my Master's project in Manchester all those years ago. Without his extensive knowledge and time, none of this thesis would be possible. But he has also taught me much about non-mathematical topics and, for that, I will always be grateful. I could not have asked for a better supervisor. I would also like to thank Kenneth Falconer for uncountable interesting mathematical conversations and for providing much feedback on several papers and this thesis. I would also like to thank the EPSRC for funding me with the Doctoral Training Grant
(EP/N509759/1).

Like the many analysis PhD students from St Andrews that have come before me, I would like to thank all the inhabitants of the bunker, this includes Amlan, Ewa, Han, Lawrence, Liam, Sascha, Stuart and Vuksan. Along with the rest of the analysis group - Mike, Lars, Collin, Tom Kempton and Jonathan Hickman - lunches and Whey Pat trips were always bright and fun times, sometimes even educational!

For 2 years I had the pleasure of sharing Muckross Flat 4 with a number of individuals and thoroughly loved that time. I would like to thank all of these flatmates, with a special place in my heart reserved for Ashley and Felix. 

Over the past few years I have met many different mathematicians and learnt much from them. Our collaboration with Antti was a particularly enjoyable experience, despite some amount of stress at the end. The Manchester analysis and dynamics group have always been my second home, welcoming me in whenever I was around. Specifically Charles who has been putting up with me for 8 years now.

Finally I would like to thank my family and friends for being behind me every step of the way, especially Sean and Amber. To anyone else reading this, I apologize for missing you out, you're breathtaking.


